---
title: "Hulp bij oplossen errors check-functies forrescalc
author: "Anja Leyman"
date: "`r Sys.Date()`"
output: 
  html_document:
    keep_md: FALSE
    number_sections: yes
    fig_caption: yes
    code_folding: hide
    toc: TRUE
    toc_float:
      collapsed: TRUE
      smooth_scroll: FALSE
---

```{r Setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = FALSE,
  message = FALSE,
  warning = FALSE, 
  fig.width = 9,
  fig.align = TRUE)

library(here)
library(sf)

# libraries & invoergegevens
source(here::here("scripts/Setup.R"))

```


```{r testdb, eval = FALSE}

path_to_testdb <- "C:/03_BR/2_Forrescalc/inst/example/testdb/mdb_bosres_test.sqlite"
path_to_testdb <-
  system.file("example/testdb/mdb_bosres_test.sqlite", package = "forrescalc")

path_to_fieldmapdb <- "C:/R/library/forrescalc/example/database/mdb_bosres.sqlite"
path_to_fieldmapdb <- path_to_testdb
```

```{r}
plotinfo <- load_plotinfo(path_to_fieldmap_db)
names(plotinfo)

test <- c("forest_reserve", "plot_id", "plottype",
        "period", "survey_number", "year_dendro",
        "survey_trees", "survey_deadw", "survey_lis",
        "survey_veg", "survey_reg",
        "game_impact_veg", "game_impact_reg", "data_processed",
        "r_A1", "r_A2", "r_A3", "r_A4", "dbh_min_a3_alive", "dbh_min_a3_dead",
        "dbh_min_a4_alive", "dbh_min_a4_dead", "dbh_min_core_area",
        "dbh_min_core_area_dead", "diam_min_a4_logs", "diam_min_core_area_logs",
        "diam_min_lis", "length_transect_lis", "length_core_area_m",
        "width_core_area_m", "core_area_ha"
        )

waldo::compare(names(plotinfo), test)

# load_plotinfo
```



```{r fctie_check_plotdetails}
check_data_plotdetails <- function(database, forest_reserve = "all") {
  selection <-
    ifelse(
      forest_reserve == "all", "",
      paste0("WHERE pd.ForestReserve = '", forest_reserve, "'")
    )
  query_plotdetails <-
    "SELECT pd.IDPlots As plot_id,
      qPlotType.Value3 AS plottype,
      pd.ForestReserve AS forest_reserve,
      pd.Survey_Trees_YN AS survey_trees,
      pd.Survey_Deadwood_YN AS survey_deadw,
      pd.Survey_Regeneration_YN AS survey_reg,
      pd.Survey_Vegetation_YN AS survey_veg,
      pd.Date_Dendro_%1$deSet AS date_dendro,
      pd.FieldTeam_Dendro_%1$deSet AS fieldteam,
      pd.rA1 AS ra1,
      pd.rA2 AS ra2,
      pd.rA3 AS ra3,
      pd.rA4 AS ra4,
      pd.LengthCoreArea_m AS length_core_area_m,
      pd.WidthCoreArea_m AS width_core_area_m,
      pd.Area_ha AS area_ha
    FROM (Plots
        INNER JOIN Plotdetails_%1$deSet pd ON Plots.ID = pd.IDPlots)
      INNER JOIN qPlotType ON Plots.Plottype = qPlotType.ID
    %3$s;"

  query_plotdetails_1986 <- sprintf(
    "SELECT pd.IDPlots As plot_id,
      qPlotType.Value3 AS plottype,
      pd.ForestReserve AS forest_reserve,
      pd.Survey_Trees_YN AS survey_trees,
      pd.Survey_Deadwood_YN AS survey_deadw,
      pd.Survey_Regeneration_YN AS survey_reg,
      pd.Survey_Vegetation_YN AS survey_veg,
      pd.Date_Dendro_1986 AS date_dendro,
      pd.FieldTeam_Dendro_1eSet AS fieldteam,
      pd.rA1 AS ra1,
      pd.rA2 AS ra2,
      pd.rA3 AS ra3,
      pd.rA4 AS ra4,
      pd.LengthCoreArea_m AS length_core_area_m,
      pd.WidthCoreArea_m AS width_core_area_m,
      pd.Area_ha AS area_ha
    FROM (Plots
        INNER JOIN Plotdetails_1986 pd ON Plots.ID = pd.IDPlots)
      INNER JOIN qPlotType ON Plots.Plottype = qPlotType.ID
    %1$s;",
    selection
  )

  data_plotdetails <-
    query_database(database, query_plotdetails, selection = selection)
  con <- connect_to_database(database)
  data_plotdetails_1986 <- dbGetQuery(con, query_plotdetails_1986) %>%
    mutate(period = 0)
  if (nrow(data_plotdetails_1986) > 0) {
    if (inherits(con, "SQLiteConnection")) {
      data_plotdetails_1986 <- data_plotdetails_1986 %>%
        mutate(
          date_dendro = as.POSIXct(.data$date_dendro, origin = "1970-01-01")
        )
    }
    data_plotdetails <- data_plotdetails %>%
      bind_rows(
        data_plotdetails_1986
      )
  }
  dbDisconnect(con)

  incorrect_plotdetails <- data_plotdetails %>%
    group_by(.data$forest_reserve, .data$period, .data$plottype) %>%
    mutate(
      forest_reserve_date = median(.data$date_dendro)
    ) %>%
    ungroup() %>%
    mutate(
      field_forest_reserve =
        ifelse(is.na(.data$forest_reserve), "missing", NA),
      field_date_dendro =
        ifelse(is.na(.data$date_dendro) &
                 (survey_trees == 10 | survey_deadw == 10)
               , "missing", NA),
      field_date_dendro =
        ifelse(
          is.na(.data$field_date_dendro) &
            year(.data$date_dendro) != year(.data$forest_reserve_date),
          "deviating",
          .data$field_date_dendro
        ),
      field_fieldteam = ifelse(is.na(.data$fieldteam) &
                                 (survey_trees == 10 | survey_deadw == 10)
                               , "missing", NA),
      field_ra1 =
        ifelse(is.na(.data$ra1) & .data$plottype == "CP" & survey_reg == 10
               , "missing", NA),
      field_ra2 =
        ifelse(is.na(.data$ra2) & .data$plottype == "CP" & survey_reg == 10
               , "missing", NA),
      field_ra3 =
        ifelse(is.na(.data$ra3) & .data$plottype == "CP" &
                 (survey_trees == 10 | survey_deadw == 10)
               , "missing", NA),
      field_ra4 =
        ifelse(is.na(.data$ra4) & .data$plottype == "CP" &
                 (survey_trees == 10 | survey_deadw == 10)
               , "missing", NA),
      field_length_core_area_m =
        ifelse(
          is.na(.data$length_core_area_m) & .data$plottype == "CA" &
            (survey_trees == 10 | survey_deadw == 10
             | survey_reg == 10 | survey_veg == 10)
          , "missing",
          NA
        ),
      field_width_core_area_m =
        ifelse(
          is.na(.data$width_core_area_m) & .data$plottype == "CA" &
            (survey_trees == 10 | survey_deadw == 10
             | survey_reg == 10 | survey_veg == 10)
          , "missing",
          NA
        ),
      field_area_ha =
        ifelse(is.na(.data$area_ha) & .data$plottype == "CA" &
                 (survey_trees == 10 | survey_deadw == 10
                  | survey_reg == 10 | survey_veg == 10)
               , "missing", NA)
    ) %>%
    select(-survey_trees, -survey_deadw, -survey_reg, -survey_veg) %>%
    pivot_longer(
      cols = c(starts_with("field_")),
      names_to = "aberrant_field",
      values_to = "anomaly",
      values_drop_na = TRUE
    ) %>%
    mutate(
      aberrant_field = gsub("^field_", "", .data$aberrant_field),
      plottype = NULL,
      forest_reserve = NA_character_,
      date_dendro = as.character(.data$date_dendro),
      fieldteam = as.character(.data$fieldteam),
      forest_reserve_date = NULL,
      across(starts_with("ra"), as.character),
      across(ends_with("_core_area_m"), as.character),
      area_ha = as.character(.data$area_ha)
    ) %>%
    pivot_longer(
      cols = !c("plot_id", "period", "aberrant_field", "anomaly"),
      names_to = "varname",
      values_to = "aberrant_value"
    ) %>%
    filter(.data$aberrant_field == .data$varname) %>%
    select(-"varname")

  return(incorrect_plotdetails)
}

```


describe("check_data_plotdetails", {
  check_plotdetails <- check_data_plotdetails(path_to_testdb)
  check_plotdetails <- check_plotdetails[check_plotdetails$period == 1, ]
  it("check missing data CP", {
    expect_equal(
      check_plotdetails[check_plotdetails$plot_id == 20, ],
      tibble(
        plot_id = 20,
        period = 1,
        aberrant_field =
          c("forest_reserve", "date_dendro", "fieldteam",
            "ra1", "ra2", "ra3", "ra4"),
        anomaly = "missing",
        aberrant_value = NA_character_
      )
    )
  })


```{r}
check_plotdetails <- check_data_plotdetails(path_to_testdb)

tibble(
        plot_id = 20,
        period = 1,
        aberrant_field =
          c("forest_reserve", "date_dendro", "fieldteam",
            "ra1", "ra2", "ra3", "ra4"),
        anomaly = "missing",
        aberrant_value = NA_character_
      )


```

```{r fctie_check_deadw}
check_data_deadwood <- function(database, forest_reserve = "all") {
  selection <-
    ifelse(
      forest_reserve == "all", "",
      paste0("WHERE pd.ForestReserve = '", forest_reserve, "'")
    )
  query_deadwood <-
    "SELECT Deadwood.IDPlots AS plot_id,
      qPlotType.Value3 AS plottype,
      Deadwood.ID AS lying_deadw_id,
      Deadwood.IntactFragment AS intact_fragment,
      Deadwood.AliveDead AS alive_dead,
      Deadwood.DecayStage AS decay_stage
    FROM ((Plots
      INNER JOIN Deadwood%2$s Deadwood ON Plots.ID = Deadwood.IDPlots)
      INNER JOIN qPlotType ON Plots.Plottype = qPlotType.ID)
      INNER JOIN Plotdetails_%1$deSet pd ON Plots.ID = pd.IDPlots
    %3$s;"

  query_deadwood_diameters <-
    "SELECT dwd.IDPlots As plot_id,
      dwd.IDDeadwood%2$s AS lying_deadw_id,
      dwd.Distance_m AS distance_m,
      dwd.Diameter_mm AS diameter_mm
    FROM Deadwood%2$s_Diameters dwd;"

  data_deadwood <-
    query_database(database, query_deadwood, selection = selection)
  data_deadwood_diameters <- query_database(database, query_deadwood_diameters)

  incorrect_deadwood <- data_deadwood %>%
    left_join(
      data_deadwood_diameters %>%
        group_by(.data$plot_id, .data$lying_deadw_id) %>%
        summarise(max_diameter_mm = max(.data$diameter_mm)) %>%
        ungroup() %>%
        filter(.data$max_diameter_mm < 100) %>%
        mutate(
          field_max_diameter_mm = "too low"
        ),
      by = c("plot_id", "lying_deadw_id")
    ) %>%
    mutate(
      field_intact_fragment =
        ifelse(is.na(.data$intact_fragment), "missing", NA),
      field_intact_fragment =
        ifelse(
          !is.na(.data$intact_fragment) &
            !.data$intact_fragment %in% c(10, 20, 30), "not in lookuplist",
          .data$field_intact_fragment
        ),
      field_intact_fragment =
        ifelse(
          !is.na(.data$intact_fragment) & .data$intact_fragment == 30 &
            .data$plottype %in% c("CP", "CA"),
          "invalid for plottype",
          .data$field_intact_fragment
        ),
      field_intact_fragment =
        ifelse(
          !is.na(.data$intact_fragment) & .data$intact_fragment == 10 &
            !.data$plottype %in% c("CA", "BE"),
          "invalid for plottype",
          .data$field_intact_fragment
        ),
      field_alive_dead = ifelse(.data$alive_dead == 11, "tree alive", NA),
      field_decay_stage = ifelse(is.na(.data$decay_stage), "missing", NA),
      field_decay_stage =
        ifelse(
          !.data$decay_stage %in% c(10, 11, 12, 13, 14, 15, 16) &
            !is.na(.data$decay_stage),
          "not in lookuplist",
          .data$field_decay_stage),
      field_decay_stage =
        ifelse(
          .data$decay_stage == 16 & .data$alive_dead == 12 &
            !is.na(.data$decay_stage) & !is.na(.data$alive_dead),
          "tree not alive",
          .data$field_decay_stage)
    ) %>%
    pivot_longer(
      cols = c(starts_with("field_")),
      names_to = "aberrant_field",
      values_to = "anomaly",
      values_drop_na = TRUE
    ) %>%
    mutate(
      aberrant_field = gsub("^field_", "", .data$aberrant_field),
      plottype = NULL
    ) %>%
    pivot_longer(
      cols =
        !c("plot_id", "lying_deadw_id", "period", "aberrant_field", "anomaly"),
      names_to = "varname",
      values_to = "aberrant_value"
    ) %>%
    filter(.data$aberrant_field == .data$varname) %>%
    select(-"varname")

  return(incorrect_deadwood)
}

```

```{r check_deadw}
check_deadwood <- check_data_deadwood(path_to_testdb)

check_deadwood <- check_deadwood[check_deadwood$period == 1, ]


waldo::compare(check_deadwood[
        check_deadwood$lying_deadw_id == 11587 &
          check_deadwood$aberrant_field == "max_diameter_mm", ],
      tibble(
        plot_id = 101,
        lying_deadw_id = 11587,
        period = 1,
        aberrant_field = "max_diameter_mm",
        anomaly = "too low",
        aberrant_value = 10
      ))
    

```


```{r fctie_create_stat}
create_statistics <-
  function(
    dataset, level = c("period", "forest_reserve"), variables,
    include_year_range = FALSE, na_rm = FALSE,
    interval_information =
      suppressMessages(
        read_csv2(system.file("extdata/class_data.csv", package = "forrescalc"))
      )
  ) {

  if (has_name(dataset, "period") && length(unique(dataset$period)) > 1 &&
      !"period" %in% c(level, variables)) {
    warning(
      "Are you sure you don't want to include period in level? Your dataset has measurements in different periods." #nolint: line_length_linter
    )
  }

  assert_that(
    all(has_name(dataset, level)),
    msg = "Dataset should contain all columns that are mentioned as level."
  )

  for (variab in variables) {
    if (!has_name(dataset, variab)) {
      assert_that(is.data.frame(interval_information))
      assert_that(
        has_name(
          interval_information,
          c("var_name", "var_min", "var_max", "preferred_transformation")
        )
      )
      var_info <- interval_information %>%
        filter(.data$var_name == variab) %>%
        distinct()
      assert_that(
        nrow(var_info) > 0,
        msg = paste0(
          "The variable '", variab, "' is not present in the given dataset ",
          "and not declared in 'interval_information'.",
        )
      )
      assert_that(
        nrow(var_info) == 1,
        msg = paste0(
          "The variable '", variab, "' is declared more than once in ",
          "'interval_information' with different parameters. ",
          "Please add each 'var_name' only once in 'interval_information'."
        )
      )
      var_min <- sym(var_info$var_min)
      var_max <- sym(var_info$var_max)
      dataset <- dataset %>%
        mutate(
          logaritmic = !is.na(var_info$preferred_transformation) &
            var_info$preferred_transformation == "log",
          value =
            ifelse(
              .data$logaritmic,
              (log(!!var_min + 1e-10) + log(!!var_max)) / 2,
              (!!var_min + !!var_max) / 2
            ),
          variance =
            ifelse(
              .data$logaritmic,
              ((log(!!var_max) - log(!!var_min + 1e-10)) / (2 * 1.96)) ^ 2,
              ((!!var_max - !!var_min) / (2 * 1.96)) ^ 2
            )
        ) %>%
        nest("{variab}" := c(.data$value, .data$variance, .data$logaritmic)) %>%  # nolint: object_name_linter
        select(-!!var_min, -!!var_max)
    } else {
      dataset <- dataset %>%
        mutate(
          logaritmic = FALSE,
          value = !!sym(variab),
          variance = NA
        ) %>%
        select(-!!sym(variab)) %>%
        nest("{variab}" := c(.data$value, .data$variance, .data$logaritmic))  # nolint: object_name_linter
    }
  }

  dataset <- dataset %>%
    select(
      all_of(level), all_of(variables),
      "year"[include_year_range & has_name(dataset, "year")]
    ) %>%
    pivot_longer(cols = all_of(variables), names_to = "variable") %>%
    unnest(cols = .data$value)
  if (na_rm) {
    dataset <- dataset %>%
      filter(!is.na(.data$value)) %>%
      right_join(
        dataset %>%
          select(
            all_of(level), "variable", "logaritmic",
            "year"[include_year_range & has_name(dataset, "year")]
          ) %>%
          distinct(),
        by = c(
          level, "variable", "logaritmic",
          "year"[include_year_range & has_name(dataset, "year")]
        )
      )
  }

  statistics <- dataset %>%
    group_by_at(vars(c(level, "variable"))) %>%
    summarise(
      n_obs = n(),
      mean = mean(.data$value),
      variance = sum(.data$variance) / .data$n_obs,
      variance =
        ifelse(is.na(.data$variance), var(.data$value), .data$variance),
      lci = .data$mean - 1.96 * sqrt(.data$variance) / sqrt(n()),
      uci = .data$mean + 1.96 * sqrt(.data$variance) / sqrt(n()),
      logaritmic = unique(.data$logaritmic)
    ) %>%
    ungroup() %>%
    mutate(
      mean = ifelse(.data$logaritmic, exp(.data$mean), .data$mean),
      lci = ifelse(.data$logaritmic, exp(.data$lci), .data$lci),
      uci = ifelse(.data$logaritmic, exp(.data$uci), .data$uci)
    )

  if (include_year_range) {
    if (has_name(dataset, "year")) {
      if (!"year" %in% level) {
        statistics <- dataset %>%
          group_by_at(vars(level)) %>%
          summarise(
            min_year = min(.data$year),
            max_year = max(.data$year)
          ) %>%
          ungroup() %>%
          left_join(
            statistics,
            by = level
          )
      } else {
        warning("No year range is calculated as 'year' is given as a level (so each year has separate records).") #nolint
      }
    } else {
      warning("Add column 'year' to dataset if you want the year range to be calculated.") #nolint
    }
  }

  return(statistics)
}
```

```{r check_stat}
data_dendro <- load_data_dendrometry(path_to_fieldmapdb)
data_deadwood <- load_data_deadwood(path_to_fieldmapdb)
data_shoots <- load_data_shoots(path_to_fieldmapdb)
height_model <- load_height_models()
plotinfo <- load_plotinfo(path_to_fieldmapdb) |>
  filter(.data$plot_id %in% c(101, 11000))
results_dendrometry <-
  calculate_dendrometry(
    data_dendro, data_deadwood, data_shoots, height_model, plotinfo
  )
dataset <- results_dendrometry[["dendro_by_plot"]] |>
  right_join(plotinfo, by = c("plot_id", "plottype", "period"))
variables_for_statistics <- dataset %>%
  select(contains(c("tree", "vol")), -contains(c("survey", "40"))) |>
  names()

```

```{r}
stat <- create_statistics(dataset = dataset,
        level = c("period", "forest_reserve"),
        variables = c("number_of_trees_ha", "vol_alive_m3_ha"),
        include_year_range = TRUE)

stat_tibble <- dataset |>
        select(
          "period", "forest_reserve", "year", "number_of_trees_ha",
          "vol_alive_m3_ha"
        ) |>
        pivot_longer(
          cols = c("number_of_trees_ha", "vol_alive_m3_ha"),
          names_to = "variable",
          values_to = "mean"
        ) |>
        transmute(
          .data$period, .data$forest_reserve,
          min_year = .data$year,
          max_year = .data$year,
          .data$variable,
          n_obs = 1,
          .data$mean,
          variance = NA_real_,
          lci = NA_real_,
          uci = NA_real_,
          logaritmic = FALSE
        ) |>
        arrange(.data$period, .data$forest_reserve)

waldo::compare(stat, stat_tibble)

expect_equal(
      create_statistics(
        dataset = dataset,
        level = c("period", "forest_reserve"),
        variables = c("number_of_trees_ha", "vol_alive_m3_ha"),
        include_year_range = TRUE
      ),
      dataset |>
        select(
          "period", "forest_reserve", "year", "number_of_trees_ha",
          "vol_alive_m3_ha"
        ) |>
        pivot_longer(
          cols = c("number_of_trees_ha", "vol_alive_m3_ha"),
          names_to = "variable",
          values_to = "mean"
        ) |>
        transmute(
          .data$period, .data$forest_reserve,
          min_year = .data$year,
          max_year = .data$year,
          .data$variable,
          n_obs = 1,
          .data$mean,
          variance = NA_real_,
          lci = NA_real_,
          uci = NA_real_,
          logaritmic = FALSE
        ) |>
        arrange(.data$period, .data$forest_reserve)
    )


variables_for_statistics_ <- dataset %>%
  select(all_of(contains(c("tree", "vol")))) %>% 
           select(-contains(c("survey", "40"))) |>
  names()
```

Error (test6_create_statistics.R:93:5): create_statistics: check behaviour if NA
<evalError/missingArgError/error/condition>
Error in `paste0("The variable '", variab, "' is not present in the given dataset ", 
    "and not declared in 'interval_information'.", )`: argument is missing, with no default

```{r check_error_stat}

stat <- create_statistics(
        dataset = dataset,
        level = c("period", "forest_reserve"),
        variables = c("number_of_trees_ha", "vol_log_m3_ha"),
        include_year_range = TRUE)

stat_tibble <- 
      dataset |>
        select(
          "period", "forest_reserve", "year", "number_of_trees_ha",
          "vol_log_m3_ha"
        ) |>
        pivot_longer(
          cols = c("number_of_trees_ha", "vol_log_m3_ha"),
          names_to = "variable",
          values_to = "mean"
        ) |>
        transmute(
          period, forest_reserve,
          min_year = year,
          max_year = year,
          variable,
          n_obs = 1,
          mean,
          variance = NA_real_,
          lci = NA_real_,
          uci = NA_real_,
          logaritmic = FALSE
        ) |>
        arrange(period, forest_reserve)


waldo::compare(stat, stat_tibble)

```




