---
title: "Hulp bij oplossen errors check-functies forrescalc
author: "Anja Leyman"
date: "`r Sys.Date()`"
output: 
  html_document:
    keep_md: FALSE
    number_sections: yes
    fig_caption: yes
    code_folding: hide
    toc: TRUE
    toc_float:
      collapsed: TRUE
      smooth_scroll: FALSE
---

```{r Setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = FALSE,
  message = FALSE,
  warning = FALSE, 
  fig.width = 9,
  fig.align = TRUE)

library(here)
library(sf)

# libraries & invoergegevens
source(here::here("scripts/Setup.R"))

```


```{r testdb}

path_to_testdb <- "C:/03_BR/2_Forrescalc/inst/example/testdb/mdb_bosres_test.sqlite"
path_to_testdb <-
  system.file("example/testdb/mdb_bosres_test.sqlite", package = "forrescalc")
```

```{r fctie_check_plotdetails}
check_data_plotdetails <- function(database, forest_reserve = "all") {
  selection <-
    ifelse(
      forest_reserve == "all", "",
      paste0("WHERE pd.ForestReserve = '", forest_reserve, "'")
    )
  query_plotdetails <-
    "SELECT pd.IDPlots As plot_id,
      qPlotType.Value3 AS plottype,
      pd.ForestReserve AS forest_reserve,
      pd.Survey_Trees_YN AS survey_trees,
      pd.Survey_Deadwood_YN AS survey_deadw,
      pd.Survey_Regeneration_YN AS survey_reg,
      pd.Survey_Vegetation_YN AS survey_veg,
      pd.Date_Dendro_%1$deSet AS date_dendro,
      pd.FieldTeam_Dendro_%1$deSet AS fieldteam,
      pd.rA1 AS ra1,
      pd.rA2 AS ra2,
      pd.rA3 AS ra3,
      pd.rA4 AS ra4,
      pd.LengthCoreArea_m AS length_core_area_m,
      pd.WidthCoreArea_m AS width_core_area_m,
      pd.Area_ha AS area_ha
    FROM (Plots
        INNER JOIN Plotdetails_%1$deSet pd ON Plots.ID = pd.IDPlots)
      INNER JOIN qPlotType ON Plots.Plottype = qPlotType.ID
    %3$s;"

  query_plotdetails_1986 <- sprintf(
    "SELECT pd.IDPlots As plot_id,
      qPlotType.Value3 AS plottype,
      pd.ForestReserve AS forest_reserve,
      pd.Survey_Trees_YN AS survey_trees,
      pd.Survey_Deadwood_YN AS survey_deadw,
      pd.Survey_Regeneration_YN AS survey_reg,
      pd.Survey_Vegetation_YN AS survey_veg,
      pd.Date_Dendro_1986 AS date_dendro,
      pd.FieldTeam_Dendro_1eSet AS fieldteam,
      pd.rA1 AS ra1,
      pd.rA2 AS ra2,
      pd.rA3 AS ra3,
      pd.rA4 AS ra4,
      pd.LengthCoreArea_m AS length_core_area_m,
      pd.WidthCoreArea_m AS width_core_area_m,
      pd.Area_ha AS area_ha
    FROM (Plots
        INNER JOIN Plotdetails_1986 pd ON Plots.ID = pd.IDPlots)
      INNER JOIN qPlotType ON Plots.Plottype = qPlotType.ID
    %1$s;",
    selection
  )

  data_plotdetails <-
    query_database(database, query_plotdetails, selection = selection)
  con <- connect_to_database(database)
  data_plotdetails_1986 <- dbGetQuery(con, query_plotdetails_1986) %>%
    mutate(period = 0)
  if (nrow(data_plotdetails_1986) > 0) {
    if (inherits(con, "SQLiteConnection")) {
      data_plotdetails_1986 <- data_plotdetails_1986 %>%
        mutate(
          date_dendro = as.POSIXct(.data$date_dendro, origin = "1970-01-01")
        )
    }
    data_plotdetails <- data_plotdetails %>%
      bind_rows(
        data_plotdetails_1986
      )
  }
  dbDisconnect(con)

  incorrect_plotdetails <- data_plotdetails %>%
    group_by(.data$forest_reserve, .data$period, .data$plottype) %>%
    mutate(
      forest_reserve_date = median(.data$date_dendro)
    ) %>%
    ungroup() %>%
    mutate(
      field_forest_reserve =
        ifelse(is.na(.data$forest_reserve), "missing", NA),
      field_date_dendro =
        ifelse(is.na(.data$date_dendro) &
                 (survey_trees == 10 | survey_deadw == 10)
               , "missing", NA),
      field_date_dendro =
        ifelse(
          is.na(.data$field_date_dendro) &
            year(.data$date_dendro) != year(.data$forest_reserve_date),
          "deviating",
          .data$field_date_dendro
        ),
      field_fieldteam = ifelse(is.na(.data$fieldteam) &
                                 (survey_trees == 10 | survey_deadw == 10)
                               , "missing", NA),
      field_ra1 =
        ifelse(is.na(.data$ra1) & .data$plottype == "CP" & survey_reg == 10
               , "missing", NA),
      field_ra2 =
        ifelse(is.na(.data$ra2) & .data$plottype == "CP" & survey_reg == 10
               , "missing", NA),
      field_ra3 =
        ifelse(is.na(.data$ra3) & .data$plottype == "CP" &
                 (survey_trees == 10 | survey_deadw == 10)
               , "missing", NA),
      field_ra4 =
        ifelse(is.na(.data$ra4) & .data$plottype == "CP" &
                 (survey_trees == 10 | survey_deadw == 10)
               , "missing", NA),
      field_length_core_area_m =
        ifelse(
          is.na(.data$length_core_area_m) & .data$plottype == "CA" &
            (survey_trees == 10 | survey_deadw == 10
             | survey_reg == 10 | survey_veg == 10)
          , "missing",
          NA
        ),
      field_width_core_area_m =
        ifelse(
          is.na(.data$width_core_area_m) & .data$plottype == "CA" &
            (survey_trees == 10 | survey_deadw == 10
             | survey_reg == 10 | survey_veg == 10)
          , "missing",
          NA
        ),
      field_area_ha =
        ifelse(is.na(.data$area_ha) & .data$plottype == "CA" &
                 (survey_trees == 10 | survey_deadw == 10
                  | survey_reg == 10 | survey_veg == 10)
               , "missing", NA)
    ) %>%
    select(-survey_trees, -survey_deadw, -survey_reg, -survey_veg) %>%
    pivot_longer(
      cols = c(starts_with("field_")),
      names_to = "aberrant_field",
      values_to = "anomaly",
      values_drop_na = TRUE
    ) %>%
    mutate(
      aberrant_field = gsub("^field_", "", .data$aberrant_field),
      plottype = NULL,
      forest_reserve = NA_character_,
      date_dendro = as.character(.data$date_dendro),
      fieldteam = as.character(.data$fieldteam),
      forest_reserve_date = NULL,
      across(starts_with("ra"), as.character),
      across(ends_with("_core_area_m"), as.character),
      area_ha = as.character(.data$area_ha)
    ) %>%
    pivot_longer(
      cols = !c("plot_id", "period", "aberrant_field", "anomaly"),
      names_to = "varname",
      values_to = "aberrant_value"
    ) %>%
    filter(.data$aberrant_field == .data$varname) %>%
    select(-"varname")

  return(incorrect_plotdetails)
}

```


describe("check_data_plotdetails", {
  check_plotdetails <- check_data_plotdetails(path_to_testdb)
  check_plotdetails <- check_plotdetails[check_plotdetails$period == 1, ]
  it("check missing data CP", {
    expect_equal(
      check_plotdetails[check_plotdetails$plot_id == 20, ],
      tibble(
        plot_id = 20,
        period = 1,
        aberrant_field =
          c("forest_reserve", "date_dendro", "fieldteam",
            "ra1", "ra2", "ra3", "ra4"),
        anomaly = "missing",
        aberrant_value = NA_character_
      )
    )
  })


```{r}
check_plotdetails <- check_data_plotdetails(path_to_testdb)

tibble(
        plot_id = 20,
        period = 1,
        aberrant_field =
          c("forest_reserve", "date_dendro", "fieldteam",
            "ra1", "ra2", "ra3", "ra4"),
        anomaly = "missing",
        aberrant_value = NA_character_
      )


```


