---
title: "KUL - Tree data from core area's Peerdsbos and Sonian forest"
author: "Anja Leyman"
date: "`r Sys.Date()`"  
output: 
  html_document:
    keep_md: FALSE
    number_sections: yes
    fig_caption: yes
    code_folding: hide
    toc: TRUE
    toc_float:
      collapsed: FALSE
      smooth_scroll: FALSE
---

```{r Rm, eval = FALSE}
rm(list=ls())
```

```{r Setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  # eval = FALSE,
  message = FALSE,
  warning = FALSE, 
  fig.width = 9,
  fig.align = TRUE)

#rm(list = ls())

# library(tidyr)
# library (rlang)
# library(dplyr)
# library(RODBC)
# library(lubridate)
# library(knitr)
# library(here)
# library(openssl)
# library(kableExtra)
# library(stringr)
# library(forrescalc)
# library(tibble)


source(here::here("scripts/Setup.R"))  # libraries, basic functions & paths
```

```{r Path}
path_to_request <- paste0(path_to_datarequests, "KUL_ArnoLeenknegt_MargoVerhulst_2022-02-18/")
```


# Request

Dit script zet de data samen zoals aangevraagd door Arno Leenknegt in het kader van zijn master thesis: "Deep learning-based mapping of tree density and species diversity in Flemish forests using Sentinel imagery".

Het kadert ook in the PhD study "Deep learning for environmental monitoring by transforming earth observation data into geo-indicators" by Margot Verhulst, with promotor prof. Ben Somers (department Earth and Environmental Sciences).

The Field data will be used as ‘ground truth data’ for the testing of deep learning algorithms to
derive forest parameters (species richness, density,...) based on high-resolution aerial
photographs and Sentinel satellite data.


## Concreet

**Plots** 
Locations and timings (core areas)* - Location Timing   

- Peerdsbos: Large core area (10ha) - 2017
- Sonian forest: Large core area (10.75ha) - 2010**, 2020
- Standard Core Area ‘Harras’ : 70x140m - 2018/19

*Ideally, some extra locations can be received in a later stage  
**The latest dataset(2020) is most important, but if possible also useful to have the 2010 data,  
as this is bit closer to high resolution aerial data that is available from 2013-2015  


**Tree level data**  

(1) Living trees  

- Geo referenced location of all trees with DBH>5cm   
--> This is the main attribute of interest, i.e. to match with aerial datasets

- DBH  
--> Possibly to filter out trees with DBH<x, or for explainability
which trees are e.g. often not detected

- CalcHeight   
--> This seems to us the best attribute to limit ourselves to trees 
from the upper canopy (which are thus present in aerial data), 
using CalcHeight > ⅔ Canopy Height***  

- IUFRO-vitality 
--> Useful to immediately know the height class(Upper canopy)

- Vitality class 
--> may be useful for explaining false positives

- Species determination 
--> To understand the composition of the forest, and to make sure
balanced datasets can be made for training and testing. Also
for explainability of possible deficiencies in performance.

- Loss of crownvolume (4 loss categories)
--> Useful to explain false positives


(2) Standing dead trees (complete tree)  

- Geo referenced location of all trees with DBH>5cm, height>1.3m  
--> Useful to explain false positives

- DBH  
--> Idem dito as for living trees

- CalcHeight  
--> Only if available


***Canopy Height: how is this determined? Can you provide the rule/formula, or Is this an
attribute available in the database (referring to 3x3 IUFRO-vitality class)?


## Voorstel

Cfr. mails 18/2/2022:

We stellen voor om eerst de drie genoemde datasets te bezorgen:   

- Kernvlakte Peerdsbos --> plot_id 400000 - period 2 (2017)  
- Kernvlakte Zoniën - opmeting 2010 --> plot-id 11000 - period 2  
- Kernvlakte Zoniën - opmeting 2020 --> plot-id 11000 - period 3  

Voor deze laatste dataset: deze is nog in verwerking, dus is het mogelijk dat bepaalde parameters (calculated height) nog ontbreken, maar de boomvoetenkaart met tree positions, species, DBH, IUFRO-class social position (dominant - medeheersend - onderdrukt) kunnen wel al aangeleverd worden.


( Ev. ook nog 
- Kernvlakte Harras --> plot-id 12000 - period 2
!! veel kleiner, niet zo interessant)



# Load data

<!-- Onderstaande tabel geeft een overzicht van de gegevens die gebruikt worden voor de analyse.   -->

```{r DataOverview, results="markup"}
data_overzicht <- data.frame(
  tabelnaam = c(dbFieldmap, "tblTreeSpeciesCharacteristics_BR.csv", dbStrata),
  locatie = c(path_to_fieldmap, paste (here::here("Data/ExterneData")), path_to_strata),
  md5 = c(md5(path_to_fieldmap), md5("tblTreeSpeciesCharacteristics_BR.csv"), md5(path_to_strata))
)

data_overzicht %>%
  kable() %>%
  kable_styling()

#dbAnalyseDataTxt <- substring(dbAnalyseData, regexpr("/", dbAnalyseData) + 1)  # voor gebruik bij wegschrijven naar resultatendb

```


```{r load_treecharact}
TreeCharact <- read.csv2(paste (here::here("Data/ExterneData"), "/tblTreeSpeciesCharacteristics_BR.csv", sep = ""))
str(TreeCharact)

```


```{r load_lkplists}
con <- odbcConnectAccess2007(path_to_fieldmap_db)

  qIndShootCop <- sqlFetch(con, "qIndShootCop", stringsAsFactors = FALSE)
  qAliveDead <- sqlFetch(con, "qAliveDead", stringsAsFactors = FALSE)
  qSpecies <- sqlFetch(con, "qAliveDead", stringsAsFactors = FALSE)
  qDecaystage <- sqlFetch(con, "qdecaystage", stringsAsFactors = FALSE)
  qIntactSnag <- sqlFetch(con, "qIntactSnag", stringsAsFactors = FALSE)
    
  qCrownVolRedu <- sqlFetch(con, "qCrownVolRedu", stringsAsFactors = FALSE)
  qBranchLenghtReduction <- sqlFetch(con, "qBranchLenghtReduction", stringsAsFactors = FALSE)

  qiufroheight <- sqlFetch(con, "qiufroheight", stringsAsFactors = FALSE)
  qiufroheight_shoots <- sqlFetch(con, "qiufroheight_shoots", stringsAsFactors = FALSE)
  qiufrovitality <- sqlFetch(con, "qiufrovitality", stringsAsFactors = FALSE)
  qiufrovitality_shoots <- sqlFetch(con, "qiufrovitality_shoots", stringsAsFactors = FALSE)
  qiufrosocialstatus <- sqlFetch(con, "qiufrosocialstatus", stringsAsFactors = FALSE)
  qiufrosocialstatus_shoots <- sqlFetch(con, "qiufrosocialstatus_shoots", stringsAsFactors = FALSE)
  
odbcClose(con)

# Soms makkelijker vanuit forresdat

# qIndShootCop <- read_vc(file = "qIndShootCop", root = path_to_forresdat_data)
# qAliveDead <- read_vc(file = "qAliveDead", root = path_to_forresdat_data)
# qDecaystage <- read_vc(file = "qdecaystage", root = path_to_forresdat_data)
# qIntactSnag <- read_vc(file = "qIntactSnag", root = path_to_forresdat_data)
# qSpecies <- read_vc(file = "qSpecies", root = path_to_forresdat_data)


```


```{r load_plotinfo}
# XY-plot

con <- odbcConnectAccess2007(path_to_strata_db)
 strata_tables <- sqlTables(con) %>% filter(!str_detect(TABLE_NAME, "MSys"))
 # strata <- sqlFetch(con, "strata_remaining", stringsAsFactors = FALSE)
 location <- sqlFetch(con, "strata_location", stringsAsFactors = FALSE)
 plotinfo <- sqlFetch(con, "info_survey", stringsAsFactors = FALSE)
odbcClose(con)

```

<br>

# File 1: plot_data

- plot/reserve ID       x                                                          
- inventory years  x                                                              
- plot coordinates x
- dbh measurement threshold  x


```{r create_plot_data_11000}
names(plotinfo)

plot_data_11000 <- plotinfo %>%   # one record per year
  filter(Unieknr == 11000 & period %in% c(2,3)) %>%  
  left_join(location %>% select(-SiteName, -SubArea), by = c("Unieknr", "plot_id")) %>% 
  # left_join(strata %>% select(-Unieknr), by = c("plot_id")) %>% 
  select(plot_id, forest_reserve, plottype, plottype_txt, 
         # SiteName, SubArea,
         # Site_subsite, 
         period, survey_number, year, date_dendro,
         TresHoldDBH_CoreArea_alive_mm, TresHoldDBH_CoreArea_dead_mm, 
         XY_co, XLambert72, YLambert72, Z_m_TAW, LatLon_co, XLon_wgs84, YLat_wgs84
         ) 

names(plot_data_11000)
summary(plot_data_11000)

# ? NA's
which(is.na(plot_data_11000), arr.ind=TRUE)
```


```{r create_plot_data_400000}
# Peerdsbos - geen plotdetails, dus ook niet in plotinfo
plot_data_400000 <- location %>%   # one record per year
  filter(Unieknr == 400000) %>%  
  # left_join(location %>% select(-SiteName, -SubArea), by = c("Unieknr", "plot_id")) %>% 
  # left_join(strata %>% select(-Unieknr), by = c("plot_id")) %>% 
  mutate(forest_reserve = "Peerdsbos", 
         plottype = 30, plottype_txt = "core area", 
         period = 2, survey_number = 1, year = survey_Y1, 
         date_dendro = "26/10/2017",
         TresHoldDBH_CoreArea_alive_mm = 150, 
         TresHoldDBH_CoreArea_dead_mm = 150, 
         ) %>% 
  select(plot_id, 
         forest_reserve, 
         plottype, plottype_txt, 
         # SiteName, SubArea,
         # Site_subsite, 
         period, survey_number, year, 
         date_dendro,
         TresHoldDBH_CoreArea_alive_mm, TresHoldDBH_CoreArea_dead_mm, 
         XY_co, XLambert72, YLambert72, Z_m_TAW, LatLon_co, XLon_wgs84, YLat_wgs84
         ) 

names(plot_data_400000)
names(plot_data_11000)

plot_data <- rbind(plot_data_11000, plot_data_400000)

# ? NA's
which(is.na(plot_data), arr.ind=TRUE)

```

<br>

# File 2: tree_data

## Variabelen

- tree ID  x 
- plot/reserve ID  
- species  x
- tree coordinates    
-	alive/dead  x
- dbh  x 
- CalcHeight   
- IUFRO-vitality 
- broken / whole tree (snags)  x
- height of broken standing deadwood   = bij snags height_m ipv calc_height  x
- decay class  x 
- Loss of crownvolume (4 loss categories)


## Hoe omgaan met hakhoutstoven?

Ik bezorg data op tree level.
Er is geen link nodig tussen periodes. 
Hakhout vormt dus geen probleem.


## Practisch

### Load trees

```{r trees_from_dbEls}
# plot 11000 - period 2&3 

# trees_calc <- read_csv2(paste0(path_to_treelevel_csv, "trees_calc.csv")) 
# trees_calc bevat niet alle gevraagde velden

# initiele functie load_data_dendrometry berekent direct lokale X en Y, wat voor kernvlaktes niet nodig is => functie aangepast

      # trees_11000 <- load_data_dendrometry(database = path_to_fieldmap_db, 
      #                                      plottype = 'Core area', forest_reserve = "Kersselaerspleyn",
      #                                      extra_variables = TRUE) %>% 
      #   filter(period %in% c(2,3)) 
      # names(trees_11000)


# XY niet lokaal

trees_11000 <- load_data_dendrometry_all(database = path_to_fieldmap_db, 
                                     plottype = 'Core area', forest_reserve = "Kersselaerspleyn",
                                     extra_variables = TRUE) %>% 
  # filter(plot_id == 11000 & period %in% c(2,3)) %>% 
  filter(period %in% c(2,3))

names(trees_11000)
```


```{r trees_from_moederdb_no_height}
# plot 400000 - period 2 
# bevat gene plotdetails => functie load_data_dendro aangepast zodat ook de plots zonder plotdetails geselecteerd werden
path_to_moederdb <- "C:/03_BR/8_Moederdatabank_tmp/MDB_BR_X8_inbo2020/FieldMapData_MDB_BR_X8_inbo2020.accdb"

trees_400000 <- load_data_dendrometry_all(database = path_to_moederdb, 
                                     # plottype = 'Core area', forest_reserve = "Peerdsbos",
# plottype en forest_reserve komen uit plotdetails en zijn niet ingevuld voor Peerdsbos (geen deel van monitoringnetwerk)
                                     extra_variables = TRUE) %>% 
  filter(plot_id == 400000 & period == 2) 

names(trees_400000)
range(trees_400000$X_m)
```


### Select variables

```{r select_variables_trees_11000}
colnames(trees_11000)

tree_data_11000 <- trees_11000 %>% 
  mutate(height_snag = ifelse(intact_snag == 10, height_m, NA)) %>% 
  rename(alive_dead_cde = alive_dead,
         ind_sht_cop_cde = ind_sht_cop,
         intact_snag_cde = intact_snag,
         decaystage_cde = decaystage,
         iufro_hght_cde = iufro_hght,
         iufro_vital_cde = iufro_vital,
         iufro_socia_cde = iufro_socia
  ) %>% 
  mutate(
      alive_dead = ifelse (alive_dead_cde == 11, "alive",
                           ifelse(alive_dead_cde == 12, "dead", NA)),
      tree_multistemmed = ifelse (ind_sht_cop_cde %in% c(10, 11), "no",
                           ifelse(ind_sht_cop_cde == 12, "yes", NA)),
      intact_snag = ifelse (intact_snag_cde == 10, "snag",
                           ifelse(intact_snag_cde == 11, "intact", NA))
      ) %>% 
  left_join(qDecaystage %>% select(ID, decaystage = Value2), by = c("decaystage_cde" = "ID")) %>% 
  left_join(TreeCharact, by = c("species" = "IDTreeSp")) %>% 
  left_join(qiufroheight %>% select(ID, iufro_hght = Value1), by = c("iufro_hght_cde" = "ID")) %>% 
  left_join(qiufrovitality %>% select(ID, iufro_vital = Value1), by = c("iufro_vital_cde" = "ID")) %>% 
  left_join(qiufrosocialstatus %>% select(ID, iufro_socia = Value1), by = c("iufro_socia_cde" = "ID")) %>%
  select(plot_id, 
       tree_measure_id, old_id, coppice_id,
       X_m, Y_m, 
       period, 
       species, NameSc, Genus, Spec, LH_NH,
       dbh_mm, height_m, calc_height_fm, height_snag, 
       tree_number, 
       alive_dead_cde, alive_dead, ind_sht_cop_cde, tree_multistemmed, 
       intact_snag_cde, intact_snag, decaystage_cde, decaystage,
       iufro_hght_cde, iufro_hght, 
       iufro_vital_cde, iufro_vital,
       iufro_socia_cde, iufro_socia,
       crown_volume_reduction, branch_length_reduction
        ) %>% 
  select(-old_id)

str(tree_data_11000)

summary(tree_data_11000)

```


```{r check_height_11000}
# normaal enkel bij period 2 calc_height_fm

check <- tree_data_11000 %>% 
  group_by(period) %>% 
  summarize(height = first(calc_height_fm)) %>% 
  ungroup()

tree_data_11000 %>% filter(period== 2 & is.na(calc_height_fm))
tree_data_11000 %>% filter(period== 2 & !is.na(calc_height_fm)) %>% nrow()

# 2 van de 3297 hebben geen hoogte
# tijdelijk overnemen van de andere calc_heights
tree_data_11000_ <- tree_data_11000 %>% 
  mutate(calc_height_fm = ifelse(is.na(calc_height_fm) & period == 2 & dbh_mm == 200,
                                 20.67,
                                 calc_height_fm),
         calc_height_fm = ifelse(is.na(calc_height_fm) & period == 2 & dbh_mm == 195,
                                 20.23,
                                 calc_height_fm)
  )
        
tree_data_11000 <- tree_data_11000_
```


```{r select_variables_trees_400000}
colnames(trees_400000)

tree_data_400000 <- trees_400000 %>% 
  mutate(height_snag = ifelse(intact_snag == 10, height_m, NA)) %>% 
  rename(alive_dead_cde = alive_dead,
         ind_sht_cop_cde = ind_sht_cop,
         intact_snag_cde = intact_snag,
         decaystage_cde = decaystage,
         iufro_hght_cde = iufro_hght,
         iufro_vital_cde = iufro_vital,
         iufro_socia_cde = iufro_socia
  ) %>% 
  mutate(
      alive_dead = ifelse (alive_dead_cde == 11, "alive",
                           ifelse(alive_dead_cde == 12, "dead", NA)),
      tree_multistemmed = ifelse (ind_sht_cop_cde %in% c(10, 11), "no",
                           ifelse(ind_sht_cop_cde == 12, "yes", NA)),
      intact_snag = ifelse (intact_snag_cde == 10, "snag",
                           ifelse(intact_snag_cde == 11, "intact", NA))
      ) %>% 
  left_join(qDecaystage %>% select(ID, decaystage = Value2), by = c("decaystage_cde" = "ID")) %>% 
  left_join(TreeCharact, by = c("species" = "IDTreeSp")) %>% 
  left_join(qiufroheight %>% select(ID, iufro_hght = Value1), by = c("iufro_hght_cde" = "ID")) %>% 
  left_join(qiufrovitality %>% select(ID, iufro_vital = Value1), by = c("iufro_vital_cde" = "ID")) %>% 
  left_join(qiufrosocialstatus %>% select(ID, iufro_socia = Value1), by = c("iufro_socia_cde" = "ID")) %>%
  select(plot_id, 
       tree_measure_id, old_id, coppice_id,
       X_m, Y_m, 
       period, 
       species, NameSc, Genus, Spec, LH_NH,
       dbh_mm, height_m, calc_height_fm, height_snag, 
       tree_number, 
       alive_dead_cde, alive_dead, ind_sht_cop_cde, tree_multistemmed, 
       intact_snag_cde, intact_snag, decaystage_cde, decaystage,
       iufro_hght_cde, iufro_hght, 
       iufro_vital_cde, iufro_vital,
       iufro_socia_cde, iufro_socia,
       crown_volume_reduction, branch_length_reduction
        ) %>% 
  select(-old_id, -coppice_id, -tree_number, # geen hakhout
         -crown_volume_reduction, -branch_length_reduction,
         -contains("iufro"))

str(tree_data_400000)
summary(tree_data_400000)

# correctie snags - enkel dan hoogte opgemeten
tree_data_400000_ <- tree_data_400000 %>% 
  mutate(intact_snag = ifelse(!is.na(height_m), "snag", intact_snag),
         intact_snag_cde = ifelse(!is.na(height_m), 10, intact_snag_cde),
         height_snag = ifelse(intact_snag_cde == 10, height_m, NA)
         )

tree_data_400000 <- tree_data_400000_
```



# Wegschrijven output

De resultaten worden weggeschreven naar csv.

```{r WegschrijvenOutput, eval = FALSE}
write.csv2(plot_data, paste0(path_to_request, "Output_R/plot_data_2022-02-23.csv"))

write.csv2(tree_data_11000, paste0(path_to_request, "Output_R/tree_data_Kerss_2022-02-23.csv"))
write.csv2(tree_data_400000, paste0(path_to_request, "Output_R/tree_data_Peerdsbos_2022-02-23.csv"))
```

