---
title: "Wildcard - Flemish forest reserve network"
subtitle: "Queries"
author: "Anja Leyman"
date: "25/02/2025"  
output: 
  html_document:
    keep_md: FALSE
    number_sections: yes
    fig_caption: yes
    code_folding: hide
    toc: TRUE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
---

```{r Rm, eval = FALSE}
rm(list=ls())
```

```{r Setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE, 
  fig.width = 7,
  fig.height = 3,
  fig.align = TRUE)

library(here)
library(writexl)
library(scales)
library(sf)


# libraries & invoergegevens
source(here::here("scripts/Setup.R"))
```


```{r Setup2}
# path_to_project <- "C:/03_BR/3_AanvraagGegevens/INBO_DigitaalVlaanderen"
path_to_project_teamdrive <- paste0(path_to_output_gdrive, "EUFORIA_WILDCARD_2024")

# path_to_datarequest <- paste0(path_to_project, "/output/")
path_to_datarequest_teamdrive <- paste0(path_to_project_teamdrive, "/output_R/")
path_to_html_teamdrive <- path_to_datarequest_teamdrive
# path_to_html <- path_to_datarequest

path_to_datacontrol <- paste0(path_to_project_teamdrive, "/datacontrole/")

```

<!-- De eerste analyse gebeurde op de fieldmapdb van 13/6/2024,  -->
<!-- maar in db van 5/12/2024 zijn de 4 sites van Zoniën duidelijk afgelijnd,  -->
<!-- dus moeten we toch van de meest recente db vertrekken (MDB_BR_X8_inbo2020_20241205) -->

```{r TEMP_db}
# path_to_fieldmap <- paste0(path_to_databases, "MDB_BR_X8_inbo2020_20240613/")
path_to_fieldmap <- paste0(path_to_databases, "MDB_BR_X8_inbo2020_20241205/")

dbFieldmap <- "FieldMapData_MDB_BR_X8_inbo2020.accdb"
path_to_fieldmap_db <- paste0(path_to_fieldmap, dbFieldmap)
```


# Request

This script creates the data as requested by Yannick De Win as part of the 
[Wildcard project](https://drive.google.com/drive/folders/0AHzOhlj-qFSnUk9PVA).

Data is collected over the whole of Europe. 

The script below generates all info and data according to the guidelines stipulated in this document: [DTF_Tree-Data-Template_final.xlsx](https://docs.google.com/spreadsheets/d/1jV4II-uSDDKaNNWqeBIXi6IQ_BSK_LFr?rtpof=true&usp=drive_fs)

The managed plots in the mainly non-managed forest reserves (EUFORIA-sites) are removed prior to analysis.

# Directories

- path_to_fieldmap_db is "`r path_to_fieldmap_db`"      
- path_to_project_teamdrive is "`r path_to_project_teamdrive`"      
- path_to_datarequest_teamdrive is "`r path_to_datarequest_teamdrive`"      

```{r results='hide', eval=TRUE}
path_to_fieldmap_db
# path_to_datarequest
path_to_project_teamdrive
path_to_datarequest_teamdrive

```

```{r load_data, results='hide'}
#
design <- read.table(paste0(path_to_datarequest_teamdrive, "INBO_Design.txt")
                           , sep = " ", dec = ".")

plots_ <- read.table(paste0(path_to_datarequest_teamdrive, "INBO_Plots.txt")
                           , sep = " ", dec = ".")
# only A4-circle + CA (no A3)
plots <-  plots_ %>% filter(CIRCLE_NO == 1 | is.na(CIRCLE_NO))
plots_LPI <- plots_ %>% filter(is.na(CIRCLE_NO))
plots_A3 <-  plots_ %>% filter(CIRCLE_NO == 2)
plots_A4 <-  plots_ %>% filter(CIRCLE_NO == 1)

standing <- read.table(paste0(path_to_datarequest_teamdrive, "INBO_Standing.txt")
                           , sep = " ", dec = ".")

lying <- read.table(paste0(path_to_datarequest_teamdrive, "INBO_Lying.txt")
                    , sep = " ", dec = ".")
```

<br>

## Important information

### Inventory year
Attention for the fact that in some reserves the inventory was spread over two consecutive years. 
So we sometimes see **two different INVENTORY YEAR's per period**.
This gives strange results for statistics per site and inventory year.

Better would be to make summary's per site and period or survey number.

### LPI-plot 11000

- Standing trees (L+D) in plot 11000 (Zonienwoud-Joseph Zwaenepoel reservaat - OldCore) 
measured in 1986 and 2000 have a treshold of 30 cm DBH (instead of 5 cm)

- In 2000 werd gebiedsdekkend gemeten vanaf 30 cm DBH, en twee groepen vanaf 5 cm.
Daarnaast streeplijsten: samen met veg in 750 subsamples: 30-20, 20-10 en < 10 cm.
Afzonderlijk verwerkt: zie `CA_Kerss_5_30_dendro_by_xxx`

```{r 11000_treshold30cm}
treshold_not_ok <- standing %>% 
  filter(LPI_ID == 11000 & DBH_mm < 300 & INVENTORY_YEAR == 2000)

```

 
- Treshold for lying deadwood measurements in 2010 and 2020 is 40 cm
- No (lying) deadwood measurements in 1986 and 2000 

<br>

# QUERIES

QUERIES_metadata	

describes basic summaries of standing, lying and CWD for each inventory year and site. 
Basic summaries (attributes) are shown in blue. 
Submit each table as a separate txt file following the same format instructions as 
for dendrometric data deliveries (see DATA_FORMAT sheet for details). 
For instance, the summaries of standing stems for the VUKOZ institute should be 
delivered as VUKOZ_STANDING_QUERY.txt.												
													
TABLE	- Enter STANDING, LYING or CWD if your data delivery includes such data.	
SITE_ID	
SITE_NAME		
WILDCARD_SUB_ID	
INVENTORY_YEAR	
INVENTORY_TYPE	Large plot inventory (LPI) or sampling plot inventory (SPI)

STEM_DENSITY: The density of standing or lying stems per one hectare in a specific inventory year and site. 
The density of standing and lying should include both living and dead stems if measured.
For SPI plots with multiple sub-circles, please calculate the sampled area of all sub-circles.

BASAL AREA: The basal area of standing stems  in m2 per one hectare in a specific inventory year and site. 
The basal area should include both living and dead stems if measured.

VOLUME_LYING: The volume of dead lying stems (deadwood) in m3 per one hectare in a specific inventory year and site.

MAX_DBH: Maximum stem DBH in mm in a specific inventory year and site.
MIN_DBH: 	Minimum stem DBH in mm in a specific inventory year and site.
MEAN_DBH: Mean stem DBH in mm in a specific inventory year and site.

MAX_D1:	Maximum D1 of lying stems in mm in a specific inventory year and site (see Lying_metadata sheet for the definition of D1).
MIN_D1:	Minimum D1 of lying stems in mm in a specific inventory year and site.
MEAN_D1:	Mean D1 of lying stems in mm in a specific inventory year and site.
MAX_D2:	Maximum D2 of lying stems in mm in a specific inventory year and site (see Lying_metadata sheet for the definition of D2).
MIN_D2:	Minimum D2 of lying stems in mm in a specific inventory year and site.
MEAN_D2:	Mean D2 of lying stems in mm in a specific inventory year and site.

CWD: NIET

## Standing table

- STEM_DENSITY (both living and dead)
- BASAL_AREA (both living and dead)
- MAX_DBH, MIN_DBH, MEAN_DBH

### Summary on plot level

STEM_DENSITY and VOLUME_HA for plots with trees

**ATTENTION**
We have to account for concentric circles and the difference between living or dead.
<!-- OPGEPAST: bij vgl met resultaten van forrescalc rekening houden met feit dat stemnr hier ook dode  -->
<!-- stammen bevat -->

```{r}
# density en volume per hectare per site, maar eerst per plot
nrow(plots_LPI) + nrow(plots_A3) + nrow(plots_A4) == nrow(plots_)
```

```{r Fext_ha_LPI_SPI}
# onderscheid A3 en AA4 circle en LPI ---------
names(standing)

## LPI
standing_LPI <- standing %>% 
  inner_join(plots_LPI, by = c("SITE_ID", "SITE_NAME", "WILDCARD_sub_ID"
                          , "INVENTORY_YEAR", "LPI_ID", "SPI_ID")) %>% 
  mutate(Fext_ha = 10000/SAMPLED_AREA) # area in m2 uitgedrukt

## SPI - A3
standing_A3 <- standing %>% 
  filter((LIFE == "A" & DBH_mm < 400) | (LIFE == "D" & DBH_mm < 100)) %>% 
  inner_join(plots_A3, by = c("SITE_ID", "SITE_NAME", "WILDCARD_sub_ID"
                          , "INVENTORY_YEAR", "LPI_ID", "SPI_ID")) %>% 
  mutate(Fext_ha = 10000/SAMPLED_AREA)

## SPI - A4
standing_A4 <- standing %>% 
  filter((LIFE == "A" & DBH_mm >= 400) | (LIFE == "D" & DBH_mm >= 100) |
           SITE_NAME %in% c("Liedekerke", "Withoefse heide")) %>% 
  inner_join(plots_A4, by = c("SITE_ID", "SITE_NAME", "WILDCARD_sub_ID"
                          , "INVENTORY_YEAR", "LPI_ID", "SPI_ID")) %>% 
  mutate(Fext_ha = 10000/SAMPLED_AREA)
  
## COMBINE
nrow(standing_LPI) + nrow(standing_A3) + nrow(standing_A4) == nrow(standing)

standing_all <- rbind(standing_LPI, standing_A3, standing_A4)
nrow(standing_all) == nrow(standing)

```


```{r}
qry_standing_per_plot <- standing_all %>% 
  mutate(stemnr_ha = Fext_ha  # !! STEMnr niet stamtal!! - ok
         , basal_area_ha = Fext_ha*pi*DBH_mm^2/4000000) %>% 
  dplyr::group_by(SITE_ID, SITE_NAME, WILDCARD_sub_ID
                  , INVENTORY_YEAR, LPI_ID, SPI_ID) %>% 
  dplyr::summarize(
    STEM_DENSITY = sum(stemnr_ha)
    , BASAL_AREA = sum(basal_area_ha)) %>% 
  ungroup()
    
head(qry_standing_per_plot)
qry_standing_per_plot %>% filter(SPI_ID == 204)
qry_standing_per_plot %>% filter(LPI_ID == 11000)
```


There are no plots without any trees

```{r eval = FALSE}
# !! ook nulwaardes meenemen
names(plots)
names(qry_standing_per_plot)

qry_standing_per_plot0 <- plots %>% 
  anti_join(qry_lying_per_plot) 

nrow(qry_standing_per_plot0) == 0

```

Calculate mean per site and inventory year

```{r}
# density en volume per hectare per site (niet per plot!
qry_standing_per_site <- qry_standing_per_plot %>% 
    mutate(INVENTORY_TYPE = ifelse(!is.na(LPI_ID), "LPI"
                                 , ifelse(!is.na(SPI_ID), "SPI", NA)
                                 )
         ) %>%
  dplyr::group_by(SITE_ID, SITE_NAME, WILDCARD_sub_ID
                  , INVENTORY_YEAR, INVENTORY_TYPE) %>% 
  dplyr::summarize(
    n_plots = n()
    , STEM_DENSITY = mean(STEM_DENSITY, na.rm = TRUE)
    , BASAL_AREA = mean(BASAL_AREA, na.rm = TRUE)) %>% 
  ungroup()
    
head(qry_standing_per_site)
```

### Overall summary of diameters

```{r}
qry_standing_diam <- standing %>% 
  mutate(INVENTORY_TYPE = ifelse(!is.na(LPI_ID), "LPI"
                                 , ifelse(!is.na(SPI_ID), "SPI", NA)
                                 )) %>% 
  group_by(SITE_ID, SITE_NAME, WILDCARD_sub_ID, INVENTORY_YEAR, INVENTORY_TYPE) %>% 
  summarize(MAX_DBH = max(DBH_mm)
            , MIN_DBH = min(DBH_mm)
            , MEAN_DBH = mean(DBH_mm)) %>% 
  ungroup()
```


### Combine

```{r}
names(qry_standing_per_site)
names(qry_standing_diam)

qry_standing_per_site <- qry_standing_per_site %>% 
  left_join(qry_standing_diam, by = c("SITE_ID", "SITE_NAME", "WILDCARD_sub_ID"
                                   , "INVENTORY_YEAR", "INVENTORY_TYPE")) %>% 
  # wegfilteren van deze waar geen opname van liggend dood hout was (Zonien 1eSET)
  filter(STEM_DENSITY != 0)  

```


##  Lying table

- STEM_DENSITY (both living and dead)
- VOLUME_LYING (dead)
- MAX_D1, MIN_D1, MEAN_D1
- MAX_D2, MIN_D2, MEAN_D2

**Attention**
Part of the lying dead wood is an "intact tree", so we only have "DBH_mm".
Therefore we added MAX_DBH, MIN_DBH, MEAN_DBH.

Another option would be to recalculate D1_mm = DBH_mm and D2_mm = 10 mm.
I leave that to Wildcard 

### Data control

```{r}
# check of D1 altijd kleiner is dan D2 - JA
check_D1D2 <- lying %>% 
  mutate(verschil_D1_D2 = D1_mm - D2_mm)
  
min(check_D1D2$verschil_D1_D2, na.rm = TRUE) == 0

```

```{r}
# 9 records met diameter < 10 cm => laten checken door Peter
error_D1D2 <- check_D1D2 %>% 
  filter(D1_mm < 100) %>% 
  select(SITE_ID, SITE_NAME, WILDCARD_sub_ID
         , LPI_ID, SPI_ID, PIECE_ID
         , INVENTORY_YEAR, TREE_SPECIES_CODE
         , contains("_mm"), LENGTH, DECAY_NUMERIC
         , verschil_D1_D2)

write_xlsx(error_D1D2, "C:/03_BR/1_DataVerwerkingBR/Output/data-validation/error_D1D2.xlsx")

```


```{r}
# tijdelijk deze records deleten
# (ook in script plot_data)
lying_ <- lying %>% 
  filter(D1_mm >= 100 | D2_mm >= 100 | DBH_mm >= 100)

nrow(lying_) == nrow(lying) - 9

lying <- lying_

```


### Summary on plot level

STEM_DENSITY and VOLUME_HA for plots with deadwood

```{r }
# density en volume per hectare per site (niet per plot!)
qry_lying_per_plot <- lying %>% 
  left_join(plots, by = c("SITE_ID", "SITE_NAME", "WILDCARD_sub_ID"
                          , "INVENTORY_YEAR", "LPI_ID", "SPI_ID")) %>% 
  mutate(stemnr_ha = 10000/SAMPLED_AREA
         , volume_ha = 10000*VOLUME/SAMPLED_AREA) %>% 
  dplyr::group_by(SITE_ID, SITE_NAME, WILDCARD_sub_ID
                  , INVENTORY_YEAR, SAMPLED_AREA
                  , LPI_ID, SPI_ID) %>% 
  dplyr::summarize(
    STEM_DENSITY = sum(stemnr_ha)
    , VOLUME_LYING = sum(volume_ha)) %>% 
  ungroup()
    
head(qry_lying_per_plot)
```

Add plots without deadwood

```{r}
# !! ook nulwaardes meenemen
names(plots)
names(qry_lying_per_plot)

qry_lying_per_plot0 <- plots %>% 
  anti_join(qry_lying_per_plot) %>% 
  select(SITE_ID, SITE_NAME, WILDCARD_sub_ID
                  , INVENTORY_YEAR, SAMPLED_AREA
                  , LPI_ID, SPI_ID) %>% 
  mutate(STEM_DENSITY = 0
         , VOLUME_LYING = 0)


nrow(qry_lying_per_plot) + nrow(qry_lying_per_plot0) == nrow(plots)

# combine
qry_lying_per_plot <- rbind(qry_lying_per_plot, qry_lying_per_plot0)
nrow(qry_lying_per_plot) == nrow(plots)
```

Calculate mean per site and inventory year

```{r}
# density en volume per hectare per site (niet per plot!
qry_lying_per_site <- qry_lying_per_plot %>% 
    mutate(INVENTORY_TYPE = ifelse(!is.na(LPI_ID), "LPI"
                                 , ifelse(!is.na(SPI_ID), "SPI", NA)
                                 )
         ) %>%
  dplyr::group_by(SITE_ID, SITE_NAME, WILDCARD_sub_ID
                  , INVENTORY_YEAR, INVENTORY_TYPE) %>% 
  dplyr::summarize(
    n_plots = n()
    , STEM_DENSITY = mean(STEM_DENSITY, na.rm = TRUE)
    , VOLUME_LYING = mean(VOLUME_LYING, na.rm = TRUE)) %>% 
  ungroup()
    
head(qry_lying_per_site)
```
### Overall summary of diameters

```{r}
qry_lying_diam <- lying %>% 
  mutate(TABLE = "LYING"
         , INVENTORY_TYPE = ifelse(!is.na(LPI_ID), "LPI"
                                 , ifelse(!is.na(SPI_ID), "SPI", NA)
                                 )
         ) %>% 
  dplyr::group_by(TABLE, SITE_ID, SITE_NAME, WILDCARD_sub_ID
                  , INVENTORY_YEAR, INVENTORY_TYPE) %>% 
  dplyr::summarize(
    MAX_D1 = max(D1_mm, na.rm = TRUE)
    , MIN_D1 = min(D1_mm, na.rm = TRUE)
    , MEAN_D1 = mean(D1_mm, na.rm = TRUE)
    , MAX_D2 = max(D2_mm, na.rm = TRUE)
    , MIN_D2 = min(D2_mm, na.rm = TRUE)
    , MEAN_D2 = mean(D2_mm, na.rm = TRUE)
    # intacte bomen
    , MAX_DBH = max(DBH_mm, na.rm = TRUE)
    , MIN_DBH = min(DBH_mm, na.rm = TRUE)
    , MEAN_DBH = mean(DBH_mm, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(MAX_DBH = ifelse(MAX_DBH == -Inf, NA, MAX_DBH)
         , MIN_DBH = ifelse(MIN_DBH == Inf, NA, MIN_DBH)
         , MEAN_DBH = ifelse(is.na(MEAN_DBH), NA, MEAN_DBH)) %>% 
  mutate_at(vars(matches("_D")), round, 0)

head(qry_lying_diam)
```

### Combine

```{r}
names(qry_lying_per_site)
names(qry_lying_diam)

qry_lying_per_site <- qry_lying_per_site %>% 
  left_join(qry_lying_diam, by = c("SITE_ID", "SITE_NAME", "WILDCARD_sub_ID"
                                   , "INVENTORY_YEAR", "INVENTORY_TYPE")) %>% 
  # wegfilteren van deze waar geen opname van liggend dood hout was (Zonien 1eSET)
  filter(STEM_DENSITY != 0)  

```







# Wegschrijven output

De resultaten worden weggeschreven naar txt (Separator = tab, Decimal =	.) en xls: 

- qry_lying_per_site.txt

- INBO_Standing.txt   

```{r final_check, eval = FALSE}
#
summary(qry_lying_per_site)

names(qry_lying_per_site)
names(qry_lying_per_site)

qry_lying_per_site %>% filter(is.na(STEM_DENSITY)) %>% nrow() == 0



```

```{r results='hide'}
# check voor NA's site-id
names(qry_lying_per_site)
col <- c("SITE_ID", "SITE_NAME", "INVENTORY_YEAR")

qry_lying_per_site %>% filter_at(col, any_vars(is.na(.))) %>% nrow() == 0

qry_standing_per_site %>% filter_at(col, any_vars(is.na(.))) %>% nrow() == 0

```


```{r WegschrijvenOutput, eval = FALSE}
# zonder extra variables  "forest_reserve_fieldmap"  forest_reserve_FM_adjusted" "plot_id" "plottype" "period" 
# extra_vars

write.table(qry_lying_per_site %>% select(-forest_reserve_FM_adjusted, -plottype, -period)
            , paste0(path_to_datarequest_teamdrive, "INBO_LYING_QUERY.txt")

write.table(qry_standing_per_site %>% select(-forest_reserve_FM_adjusted, -plottype, -period)
            , paste0(path_to_datarequest_teamdrive, "INBO_STANDING_QUERY.txt")
```



```{r WegschrijvenOutput_csv, eval = FALSE}
# idem als txt, maar voor gemak ook naar xls

write_csv2(qry_lying_per_site %>% select(-forest_reserve_FM_adjusted, -plottype, -period)
            , paste0(path_to_datarequest_teamdrive, "csv/INBO_LYING_QUERY.csv"))

write_csv2(qry_standing_per_site %>% select(-forest_reserve_FM_adjusted, -plottype, -period)
            , paste0(path_to_datarequest_teamdrive, "csv/INBO_STANDING_QUERY.csv"))
```

<br>

# Read

Checken of de geëxporteerde files goed in R ingelezen worden

```{r check_read, eval = FALSE, results='hide'}
#
qry_lying_check <- read.table(paste0(path_to_datarequest_teamdrive, "INBO_LYING_QUERY.txt")
                           , sep = " ", dec = ".")
head(qry_lying_check)
names(qry_lying_check)

#
qry_standing_check <- read.table(paste0(path_to_datarequest_teamdrive, "INBO_STANDING_QUERY.txt")
                           , sep = " ", dec = ".")
head(qry_standing_check)
names(qry_standing_check)

```

<br>

# Copy html to teamdrive

Na knitting - manueel

```{r eval = FALSE}
# Specify the path of the file you want to copy
source_file <- here::here(paste0("Scripts/AanvraagGegevens/INBO_Wildcard_EuFoRIa/Wildcard_Flanders_queries.html"))

# Specify the destination directory where you want to copy the file
destination_dir <- path_to_html_teamdrive

# Copy the file to the destination directory
file.copy(from = source_file, to = destination_dir, overwrite = TRUE)
# ? file.copy
```
