---
title: "Wildcard - Flemish forest reserve network"
subtitle: "Queries - aanvulling 2026, nieuw dataformaat"
author: "Anja Leyman"
date: "04/09/2026"  
output: 
  html_document:
    keep_md: FALSE
    number_sections: yes
    fig_caption: yes
    code_folding: hide
    toc: TRUE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
---

```{r Rm, eval = FALSE}
rm(list=ls())
```

```{r Setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  message = FALSE,
  warning = FALSE, 
  fig.width = 7,
  fig.height = 3,
  fig.align = TRUE)

library(here)
library(writexl)
library(scales)
library(sf)


# libraries & invoergegevens
source(here::here("scripts/Setup.R"))
```


```{r Setup2}
# path_to_project <- "C:/03_BR/3_AanvraagGegevens/INBO_DigitaalVlaanderen"
path_to_project_teamdrive <- paste0(path_to_output_gdrive, "EUFORIA_WILDCARD_2024")

# path_to_datarequest <- paste0(path_to_project, "/output/")
path_to_datarequest_teamdrive <- paste0(path_to_project_teamdrive, "/output_R/extra_data_2026_new_format/")
path_to_datarequest_old <- paste0(path_to_project_teamdrive
                                  , "/output_R/versie_feb2025/")
path_to_html_teamdrive <- path_to_datarequest_teamdrive
# path_to_html <- path_to_datarequest

```


# Request

This script creates the data as requested by Yannick De Win as part of the 
[Wildcard project](https://drive.google.com/drive/folders/0AHzOhlj-qFSnUk9PVA).

Data is collected over the whole of Europe. 

The script below generates all info and data according to the guidelines stipulated in this document: [DTF_Tree-Data-Template_final.xlsx](https://docs.google.com/spreadsheets/d/1jV4II-uSDDKaNNWqeBIXi6IQ_BSK_LFr?rtpof=true&usp=drive_fs)

The managed plots in the mainly non-managed forest reserves (EUFORIA-sites) are removed prior to analysis.

# Directories

- path_to_fieldmap_db is "`r path_to_fieldmap_db`"      
- path_to_project_teamdrive is "`r path_to_project_teamdrive`"      
- path_to_datarequest_teamdrive is "`r path_to_datarequest_teamdrive`"      

```{r results='hide', eval=TRUE}
path_to_fieldmap_db
# path_to_datarequest
path_to_project_teamdrive
path_to_datarequest_teamdrive

```

```{r load_data, results='hide'}
#
design <- read.table(paste0(path_to_datarequest_teamdrive, "UPLOAD_INBO_DESIGN_2026-05-07.txt")
                           , sep = "\t", dec = ".")

plots_ <- read.table(paste0(path_to_datarequest_teamdrive, "UPLOAD_INBO_PLOTS_2026-05-07.txt")
                           , sep = "\t", dec = ".")
names(plots_)
# only A4-circle + CA (no A3)
plots <-  plots_ %>% filter(circle_no == 1 | is.na(circle_no))
plots_LPI <- plots_ %>% filter(circle_no == "\\N")
plots_A3 <-  plots_ %>% filter(circle_no == 2)
plots_A4 <-  plots_ %>% filter(circle_no == 1)

# standing <- read.table(paste0(path_to_datarequest_teamdrive, "INBO_Standing.txt")
#                            , sep = " ", dec = ".")
# 
# lying <- read.table(paste0(path_to_datarequest_teamdrive, "INBO_Lying.txt")
#                     , sep = " ", dec = ".")

trees <- read.table(paste0(path_to_datarequest_teamdrive, "UPLOAD_INBO_TREES_2026-05-07.txt")
                           , sep = "\t", dec = ".")

```

<br>

# Important information

## Plots with no trees and/or no deadwood  
To calculate the mean number of trunks, mean basal area and mean volume per site and inventory year, we also took into account the plots without trees or dead wood.

Mean dbh and mean diameter_1/diameter_2 is based on all measured trees for a site and inventory year.


## Inventory year
Attention for the fact that in some reserves the inventory was spread over two consecutive years. 
So we sometimes see **two different INVENTORY YEAR's per period**.
This gives strange results for statistics per site and inventory year.

Better would be to make summary's per site and period or survey number.

## LPI-plot 11000

- Standing trees (L+D) in plot 11000 (Zonienwoud-Joseph Zwaenepoel reservaat - OldCore) 
measured in 1986 and 2000 have a treshold of 30 cm DBH (instead of 5 cm)

- Treshold for lying deadwood measurements in 2010 and 2020 is 40 cm

- No (lying) deadwood measurements in 1986 and 2000 

<br>

# QUERIES

**QUERIES_metadata**	

describes basic summaries of standing, lying and CWD for each inventory year and site. 
Basic summaries (attributes) are shown in blue. 
Submit each table as a separate txt file following the same format instructions as 
for dendrometric data deliveries (see DATA_FORMAT sheet for details). 
For instance, the summaries of standing stems for the VUKOZ institute should be 
delivered as VUKOZ_STANDING_QUERY.txt.												
													
**TABLE**	- Enter STANDING, LYING or CWD if your data delivery includes such data.	
SITE_ID	
SITE_NAME		
WILDCARD_SUB_ID	
INVENTORY_YEAR	
INVENTORY_TYPE	Large plot inventory (LPI) or sampling plot inventory (SPI)

**STEM_DENSITY:** The density of standing or lying stems per one hectare in a specific inventory year and site. 
The density of standing and lying should include both living and dead stems if measured.
For SPI plots with multiple sub-circles, please calculate the sampled area of all sub-circles.

**BASAL AREA:** The basal area of standing stems  in m2 per one hectare in a specific inventory year and site. 
The basal area should include both living and dead stems if measured.

**VOLUME_LYING:** The volume of dead lying stems (deadwood) in m3 per one hectare in a specific inventory year and site.

**DIAMETER**
MAX_DBH: Maximum stem DBH in mm in a specific inventory year and site.
MIN_DBH: 	Minimum stem DBH in mm in a specific inventory year and site.
MEAN_DBH: Mean stem DBH in mm in a specific inventory year and site.

MAX_D1:	Maximum D1 of lying stems in mm in a specific inventory year and site (see Lying_metadata sheet for the definition of D1).
MIN_D1:	Minimum D1 of lying stems in mm in a specific inventory year and site.
MEAN_D1:	Mean D1 of lying stems in mm in a specific inventory year and site.
MAX_D2:	Maximum D2 of lying stems in mm in a specific inventory year and site (see Lying_metadata sheet for the definition of D2).
MIN_D2:	Minimum D2 of lying stems in mm in a specific inventory year and site.
MEAN_D2:	Mean D2 of lying stems in mm in a specific inventory year and site.

**CWD:** NIET


## Trees

As for the format, the queries have remained largely the same, but it would be 
good to separate standing and lying queries into two different files and have 
separate rows for each circle_no 
(in case of SPIs, for LPIs the circle_no can, of course, remain empty).

Best,

Magda Guńka

```{r results='hide'}
names(trees)
str(trees)

cols_numeric <- c("dbh", "height", "length", "diameter_1", "diameter_2")
trees_ <- trees |> 
  mutate_at(cols_numeric, as.numeric)
str(trees_)
trees <- trees_

standing <- trees |> 
  filter(position == "S")
lying <- trees |> 
  filter(position == "L")
nrow(trees) == nrow(standing) + nrow(lying)
```

## Standing table

- STEM_DENSITY (both living and dead)
- BASAL_AREA (both living and dead)
- MAX_DBH, MIN_DBH, MEAN_DBH

### STEM_DENSITY and BASAL_AREA

STEM_DENSITY and BASAL_AREA for plots with standing trees

**ATTENTION**
We have to account for concentric circles and the difference between living or dead.
<!-- OPGEPAST: bij vgl met resultaten van forrescalc rekening houden met feit dat stemnr hier ook dode  -->
<!-- stammen bevat -->

```{r results='hide'}
# density en volume per hectare per site, maar eerst per plot
nrow(plots_LPI) + nrow(plots_A3) + nrow(plots_A4) == nrow(plots_)
```

```{r Fext_ha_LPI_SPI, results='hide'}
# onderscheid A3 en AA4 circle en LPI ---------

all <- standing %>% 
  inner_join(plots_, by = c("composed_site_id", "inventory_id", "inventory_type"
                               , "plot_id", "circle_no", "inventory_year"))
nrow(all) == nrow(standing)

## LPI
standing_LPI <- standing %>% 
  inner_join(plots_LPI, by = c("composed_site_id", "inventory_id", "inventory_type"
                               , "plot_id", "circle_no", "inventory_year")) %>% 
  mutate(Fext_ha = 10000/sampled_area) # area in m2 uitgedrukt

## SPI - A3
standing_A3 <- standing %>% 
  # filter((life == "A" & dbh < 400) | (life == "D" & dbh < 100)) %>% 
  # filter(!str_detect(composed_site_id, "Liedekerke|Withoefse heide")) |>   # niet nodig want zitten ook niet in plots_A3
  inner_join(plots_A3, by = c("composed_site_id", "inventory_id", "inventory_type"
                               , "plot_id", "circle_no", "inventory_year")) %>% 
  mutate(Fext_ha = 10000/sampled_area)


## SPI - A4
standing_A4 <- standing %>% 
  # filter((life == "A" & dbh >= 400) | (life == "D" & dbh >= 100) |
  #          str_detect(composed_site_id, "Liedekerke|Withoefse heide")) %>% 
  inner_join(plots_A4, by = c("composed_site_id", "inventory_id", "inventory_type"
                               , "plot_id", "circle_no", "inventory_year")) %>% 
  mutate(Fext_ha = 10000/sampled_area)

## COMBINE
nrow(standing_LPI) + nrow(standing_A3) + nrow(standing_A4) == nrow(standing)

standing_all <- rbind(standing_LPI, standing_A3, standing_A4)
nrow(standing_all) == nrow(standing)

# extra check
standing_A3 |> group_by(circle_no,life) |> 
  filter(stem_id == "\\N") |> # geen hakhout want dat kan afwijken, want circle op tree-niveau bepaald
  summarise(min_dbh= min(dbh), max_dbh = max(dbh)) |> 
  ungroup()

standing_A4 |> group_by(circle_no,life) |> 
  filter(stem_id == "\\N" & !str_detect(composed_site_id, "Liedekerke|Withoefse heide")) |> 
  summarise(min_dbh= min(dbh), max_dbh = max(dbh)) |> 
  ungroup()
```

```{r results='hide'}
qry_standing_per_plot <- standing_all %>% 
  mutate(stemnr_ha = Fext_ha  # !! STEMnr niet stamtal!! - ok
         , basal_area_ha = Fext_ha*pi*dbh^2/4000000) %>% 
  dplyr::group_by(composed_site_id, inventory_id, inventory_type, plot_id
                  , inventory_year) %>% 
  dplyr::summarize(
    STEM_DENSITY = sum(stemnr_ha)
    , BASAL_AREA = sum(basal_area_ha)) %>% 
  ungroup()
    
head(qry_standing_per_plot)
# vgl met forresdat-data: lijkt ok
qry_standing_per_plot %>% filter(plot_id == 842)
qry_standing_per_plot %>% filter(plot_id == 171100)

```

Add plots with no trees (only one SPI-plot).

```{r results='hide', eval = FALSE}
# !! ook nulwaardes meenemen - HIER NIET NODIG (30/3/2026: coolhem en terrijst 3de decade)
names(plots)
names(qry_standing_per_plot) # 181

qry_standing_per_plot0 <- plots %>% #  opgepast: enkel SPI-plots, geen LPI
  anti_join(qry_standing_per_plot)  %>% 
  select(composed_site_id, inventory_id, inventory_type, plot_id
         , inventory_year) %>% 
  mutate(STEM_DENSITY = 0
         , BASAL_AREA = 0)
# !! 0 want hier enkel de aanvulling!!!

nrow(qry_standing_per_plot) + nrow(qry_standing_per_plot0) == nrow(plots) + 5  # 5 LPI plots niet in "plots"

# combine
qry_standing_per_plot <- rbind(qry_standing_per_plot, qry_standing_per_plot0)
nrow(qry_standing_per_plot) == nrow(plots) + 5   # 5 LPI plots niet in "plots"
```

Calculate mean per site and inventory year

```{r results='hide'}
# density en volume per hectare per site (niet per plot!
qry_standing_per_site <- qry_standing_per_plot %>% 
  dplyr::group_by(composed_site_id, inventory_id, inventory_type, 
                  , inventory_year) %>% 
  dplyr::summarize(
    n_plots = n()
    , STEM_DENSITY = round(mean(STEM_DENSITY, na.rm = TRUE), 0)
    , BASAL_AREA = round(mean(BASAL_AREA, na.rm = TRUE), 2)) %>% 
  ungroup()
    
head(qry_standing_per_site)
```

### Diameters

Overall summary of diameters per site and inventory year

```{r}
qry_standing_diam <- standing %>% 
  group_by(composed_site_id, inventory_id, inventory_type, inventory_year) %>% 
  summarize(MAX_DBH = max(dbh)
            , MIN_DBH = min(dbh)
            , MEAN_DBH = mean(dbh)) %>% 
  ungroup() %>% 
  mutate_at(vars(matches("_DBH")), round, 0)
```


### Combine

```{r results='hide'}
names(qry_standing_per_site)
names(qry_standing_diam)

qry_standing_per_site <- qry_standing_per_site %>% 
  left_join(qry_standing_diam, by = c("composed_site_id", "inventory_id"
                                      , "inventory_type", "inventory_year")) 

# snelle check
qry_standing_per_site %>% filter(str_detect(composed_site_id, "Bos Terrijst") & inventory_type ==  "SPI")
qry_standing_per_site %>% filter(str_detect(composed_site_id, "Coolhembos") & inventory_type ==  "LPI")
```


##  Lying table

- STEM_DENSITY (both living and dead)
- VOLUME_LYING (dead)
- MAX_D1, MIN_D1, MEAN_D1
- MAX_D2, MIN_D2, MEAN_D2

**Attention**
Part of the lying dead wood is an "intact tree", so we only have "dbh".
Therefore we added MAX_DBH, MIN_DBH, MEAN_DBH.

Another option would be to recalculate diameter_1 = dbh and diameter_2 = 10 mm.
I leave that to Wildcard 

```{r checkD1D2, results='hide'}
names(lying)
# check of D1 altijd kleiner is dan D2 - JA
check_D1D2 <- lying %>% 
  mutate(verschil_D1_D2 = diameter_1 - diameter_2)
  
min(check_D1D2$verschil_D1_D2, na.rm = TRUE) == 0
```


### STEM_DENSITY and VOLUME_HA

STEM_DENSITY and VOLUME_HA for plots with deadwood

```{r results='hide'}
# density en volume per hectare per site (niet per plot!)
qry_lying_per_plot <- lying %>% 
  left_join(plots, by = c("composed_site_id", "inventory_id", "inventory_type"
                               , "plot_id", "circle_no", "inventory_year")) %>% 
  mutate(stemnr_ha = 10000/sampled_area
         , volume_ha = 10000*volume/sampled_area) %>% 
  dplyr::group_by(composed_site_id, inventory_id, inventory_type
                  , inventory_year, sampled_area
                  , plot_id) %>% 
  dplyr::summarize(
    STEM_DENSITY = sum(stemnr_ha)
    , VOLUME_LYING = sum(volume_ha)) %>% 
  ungroup()
    
head(qry_lying_per_plot)
```

Add plots without deadwood (dat zijn enkel SPI plots)

```{r results='hide'}
# !! ook nulwaardes meenemen
names(plots) # enkel SPI maar dat is OK, want in LPI altijd dood hout
names(qry_lying_per_plot)

qry_lying_per_plot0 <- plots %>% 
  anti_join(qry_lying_per_plot) %>% 
  select(composed_site_id, inventory_id, inventory_type
                  , inventory_year, sampled_area
                  , plot_id) %>% 
  mutate(STEM_DENSITY = 0
         , VOLUME_LYING = 0)


nrow(qry_lying_per_plot) + nrow(qry_lying_per_plot0) == nrow(plots) + 5  # 5 LPI plots

# combine
qry_lying_per_plot <- rbind(qry_lying_per_plot, qry_lying_per_plot0)
nrow(qry_lying_per_plot) == nrow(plots) + 5
```

Calculate mean per site and inventory year

```{r results='hide'}
# density en volume per hectare per site (niet per plot!
qry_lying_per_site <- qry_lying_per_plot %>% 
  dplyr::group_by(composed_site_id, inventory_id, inventory_type
                  , inventory_year) %>% 
  dplyr::summarize(
    n_plots = n()
    , STEM_DENSITY = round(mean(STEM_DENSITY, na.rm = TRUE), 0)
    , VOLUME_LYING = round(mean(VOLUME_LYING, na.rm = TRUE), 2)
    ) %>% 
  ungroup()
    
head(qry_lying_per_site)
```


### Diameters

Overall summary of diameters per site and inventory year

```{r results='hide'}
qry_lying_diam <- lying %>% 
  dplyr::group_by(composed_site_id, inventory_id, inventory_type
                  , inventory_year) %>% 
  dplyr::summarize(
    MAX_D1 = max(diameter_1, na.rm = TRUE)
    , MIN_D1 = min(diameter_1, na.rm = TRUE)
    , MEAN_D1 = mean(diameter_1, na.rm = TRUE)
    , MAX_D2 = max(diameter_2, na.rm = TRUE)
    , MIN_D2 = min(diameter_2, na.rm = TRUE)
    , MEAN_D2 = mean(diameter_2, na.rm = TRUE)
    # intacte bomen
    , MAX_DBH = max(dbh, na.rm = TRUE)
    , MIN_DBH = min(dbh, na.rm = TRUE)
    , MEAN_DBH = mean(dbh, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(MAX_DBH = ifelse(MAX_DBH == -Inf, NA, MAX_DBH)
         , MIN_DBH = ifelse(MIN_DBH == Inf, NA, MIN_DBH)
         , MEAN_DBH = ifelse(is.na(MEAN_DBH), NA, MEAN_DBH)) %>% 
  mutate_at(vars(matches("_D")), round, 0)

head(qry_lying_diam)
```

### Combine

```{r results='hide'}
names(qry_lying_per_site)
names(qry_lying_diam)

qry_lying_per_site <- qry_lying_per_site %>% 
  left_join(qry_lying_diam, by = c("composed_site_id", "inventory_id", "inventory_type"
                               , "inventory_year")) %>% 
  # wegfilteren van deze waar geen opname van liggend dood hout was (Zonien 1eSET)
  filter(STEM_DENSITY != 0)  

```

<br>

# Wegschrijven output

De resultaten worden weggeschreven naar txt (Separator = tab, Decimal =	.) en csv: 

- INBO_STANDING_QUERY.txt
- INBO_LYING_QUERY.txt

```{r final_check, eval = FALSE}
#
summary(qry_standing_per_site)
names(qry_standing_per_site)

qry_standing_per_site %>% filter(is.na(STEM_DENSITY)) %>% nrow() == 0

#
summary(qry_lying_per_site)
names(qry_lying_per_site)

qry_lying_per_site %>% filter(is.na(STEM_DENSITY)) %>% nrow() == 0

```

```{r results='hide'}
# check voor NA's site-id
names(qry_lying_per_site)
col <- c("composed_site_id", "inventory_id", "inventory_type", "inventory_year")

qry_lying_per_site %>% filter_at(col, any_vars(is.na(.))) %>% nrow() == 0

qry_standing_per_site %>% filter_at(col, any_vars(is.na(.))) %>% nrow() == 0

```


```{r WegschrijvenOutput, eval = FALSE}
write.table(qry_lying_per_site %>% select(-n_plots)
            , paste0(path_to_datarequest_teamdrive, "INBO_LYING_QUERY_", Sys.Date(), ".txt")
            , sep = "\t", na = "\\N", dec = ".")

write.table(qry_standing_per_site %>% select(-n_plots)
            , paste0(path_to_datarequest_teamdrive, "INBO_STANDING_QUERY_", Sys.Date(), ".txt")
            , sep = "\t", na = "\\N", dec = ".")
```


```{r WegschrijvenOutput_csv, eval = FALSE}
# idem als txt, maar voor gemak ook naar xls

write_csv2(qry_lying_per_site %>% select(-n_plots)
            , paste0(path_to_datarequest_teamdrive, "csv/INBO_LYING_QUERY.csv"))

write_csv2(qry_standing_per_site %>% select(-n_plots)
            , paste0(path_to_datarequest_teamdrive, "csv/INBO_STANDING_QUERY.csv"))
```

<br>

# Read

Checken of de geëxporteerde files goed in R ingelezen worden

```{r check_read, eval = FALSE, results='hide'}
#
qry_lying_check <- read.table(paste0(path_to_datarequest_teamdrive, "INBO_LYING_QUERY.txt")
                           , sep = "\t", dec = ".")
head(qry_lying_check)
names(qry_lying_check)

#
qry_standing_check <- read.table(paste0(path_to_datarequest_teamdrive, "INBO_STANDING_QUERY.txt")
                           , sep = "\t", dec = ".")
head(qry_standing_check)
names(qry_standing_check)

```

<br>

# Copy html to teamdrive

Na knitting - manueel

```{r eval = FALSE}
# Specify the path of the file you want to copy
source_file <- here::here(paste0("Scripts/AanvraagGegevens/INBO_Wildcard_EuFoRIa/Wildcard_Flanders_queries_extra2026_new_format.html"))

# Specify the destination directory where you want to copy the file
destination_dir <- path_to_html_teamdrive

# Copy the file to the destination directory
file.copy(from = source_file, to = destination_dir, overwrite = TRUE)
# ? file.copy
```
