---
title: "Json data packages - verkenning"
author: "Anja Leyman"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
editor_options: 
  chunk_output_type: inline
---

```{r Rm, eval = FALSE}
rm(list=ls())
```

```{r Setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  eval = FALSE,
  message = FALSE,
  warning = FALSE, 
  fig.width = 9,
  fig.align = TRUE)

#rm(list = ls())

library(here)

# libraries & invoergegevens
source(here::here("scripts/Setup.R"))

library(frictionless)
# library (rlang)
# library(dplyr)
# library(RODBC)
# library(lubridate)
# library(knitr)
# library(here)
# library(openssl)
# library(kableExtra)
# library(stringr)


```

# Vraagstelling

Heeft frictionless voordelen tov git2rdata

json data-package naast csv

Enkele voorbeelden doorgekregen van Els:

Voor meer voorbeelden, zie datasets gepubliceerd door [INBO op Zenodo](https://zenodo.org/communities/inbo/?q=&l=list&p=1&s=10&sort=newest), 
bv. [deze](https://zenodo.org/records/10054718) en 
[deze](https://zenodo.org/records/10054709). 
(Ik zie wel dat in deze willekeurig gekozen voorbeelden vooral .csv.gz zit, 
waarschijnlijk omdat er geodata in zitten? In elk geval kan het ook met gewone .csv, 
zoals er in het 2de voorbeeld eentje tussen zit.)

Mooi verwoord: 

Data in this package are exported from Movebank study 1259686571. 
Fields in the data follow the Movebank Attribute Dictionary and are described 
in datapackage.json. Files are structured as a Frictionless Data Package. 
You can access all data in R via https://zenodo.org/records/10054718/files/datapackage.json 
using frictionless.

- datapackage.json: technical description of the data files.   
- LBBG_JUVENILE-reference-data.csv: reference data about the animals, tags and deployments.   
- LBBG_JUVENILE-gps-yyyy.csv.gz: GPS data recorded by the tags, grouped by year.   


# Practisch

Zie [info on package](https://cran.r-project.org/web/packages/frictionless/vignettes/frictionless.html)

## Inlezen

To read a Data Package, you need to know the path or URL to its descriptor file, 
named datapackage.json. 
That file describes the Data Package, provides access points to its Data Resources 
and can contain dataset-level metadata. L
et’s read a Data Package descriptor file published on Zenodo:

```{r}
package <- read_package("https://zenodo.org/record/10054718/files/datapackage.json")
# warning is ok, standaard melding!
```
`read_package()` returns the content of datapackage.json as a list, 
printed here with `str()` to improve readability:

```{r}
str(package, list.len = 3)

str(package, list.len = 4)


```
The most important aspect of a Data Package are its Data Resources, which describe 
and point to the data. You can list all included resources with `resources()`:

```{r}
resources(package)
```

This Data Package has 3 resources. Let’s read the data from the gps resource into a data frame:


```{r}
gps <- read_resource(package, "gps")
gps
```

The data frame contains all GPS records, even though the actual data were split over 
multiple CSV zipped files. 
`read_resource()` assigned the column names and types based on the Table Schema 
that was defined for that resource, not the headers of the CSV file.

You can also read data from a local (e.g. downloaded) Data Package. In fact, there 
is one included in the frictionless pkg, let’s read that one from disk:

```{r}
local_package <- read_package(
  system.file("extdata", "datapackage.json", package = "frictionless")
)
#> Please make sure you have the right to access data from this Data Package for your intended use.
#> Follow applicable norms or requirements to credit the dataset and its authors.
read_resource(local_package, "media")
```
Data from the media was not stored in a CSV file, but directly in the data property of 
that resource in datapackage.json. 
`read_resource()` will automatically detect where to read data from.


## Aanmaken

Data Package is a good format to technically describe your data, e.g. if you are 
planning to deposit it on research repository. It also goes a long way meeting FAIR principles.

The frictionless pkg assumes your data are stored as a data frame or CSV files. 
Let’s use the built-in dataset iris as your data frame.
Create a Data Package with `create_package()` and add your data frame as a 
resource with the name iris:

```{r}
library(dplyr)
dplyr::as_tibble(iris)

my_package <-
  create_package() %>%
  add_resource(resource_name = "iris", data = iris)
```

Note that you can chain most frictionless functions together using pipes (%>% or |>), 
which improves readability.

my_package now contains one resource:

```{r}
resources(my_package)
```
By default, `add_resource()` will create a Table Schema for your data frame, 
describing its field names, field types and (for factors) constraints. 
You can retrieve the schema of a resource with `get_schema()`. 
It is a list, which we print here using `str()`:

```{r}
iris_schema <-
  my_package %>%
  get_schema("iris")

str(iris_schema)

```

You can also create a schema from a data frame, using `create_schema()`:

```{r}
iris_schema <- create_schema(iris)
```

Doing so allows you to customize the schema before adding the resource. 
E.g. let’s add a description for Sepal.Length:

```{r}
iris_schema$fields[[1]]$description <- "Sepal length in cm."
# Show result
str(iris_schema$fields[[1]])
#> List of 3
#>  $ name       : chr "Sepal.Length"
#>  $ type       : chr "number"
#>  $ description: chr "Sepal length in cm."
```
Since schema is a list, you can **use the purrr pkg to edit multiple elements at once**:

```{r}
# Remove description for first field
iris_schema$fields[[1]]$description <- NULL

# Set descriptions for all fields
descriptions <- c(
  "Sepal length in cm.",
  "Sepal width in cm.",
  "Pedal length in cm.",
  "Pedal width in cm.",
  "Iris species."
)
iris_schema$fields <- purrr::imap(
  iris_schema$fields,
  ~ c(.x, description = descriptions[.y])
)

str(iris_schema)
```

Let’s add iris as a resource to your Data Package again, but this time with the customized schema. 
Note that you have to remove the originally added resource iris with remove_resource() first, 
since Data Packages can only contain uniquely named resources:

```{r}
my_package <-
  my_package %>%
  remove_resource("iris") %>% # Remove originally added resource
  add_resource(
    resource_name = "iris",
    data = iris,
    schema = iris_schema # Your customized schema
  )
```

## Bestaande csv's toevoegen

If you already have your data stored as CSV files and you want to include them as is 
as a Data Resource, you can do so as well. As with data frames, you can opt to create a 
Table Schema automatically or provide your own.

```{r}
# Two CSV files with the same structure
path_1 <- system.file("extdata", "observations_1.csv", package = "frictionless")
path_2 <- system.file("extdata", "observations_2.csv", package = "frictionless")

path_1
# [1] "C:/R/library/frictionless/extdata/observations_1.csv"


# Add both CSV files as a single resource
my_package <-
  my_package %>%
  add_resource(resource_name = "observations", data = c(path_1, path_2))
```

Your Data Package now contains 2 resources, but you can add metadata properties as well 
(see the Data Package documentation for an overview). Since it is a list, you can use 
append() to insert properties at the desired place. Let’s add name as first and title 
as second property:

```{r}
my_package <- append(my_package, c(name = "my_package"), after = 0)
# Or with purrr::prepend(): prepend(my_package, c(name = "my_package))
my_package <- append(my_package, c(title = "My package"), after = 1)
```


Note that in the above steps you started a Data Package from scratch with `create_package()`, 
but you can use the same functionality to edit an existing Data Package read with `read_package()`.


## Add descriptions using purr

Since schema is a list, you can **use the purrr pkg to edit multiple elements at once**:

```{r}
# Remove description for first field
iris_schema$fields[[1]]$description <- NULL

# Set descriptions for all fields
descriptions <- c(
  "Sepal length in cm.",
  "Sepal width in cm.",
  "Pedal length in cm.",
  "Pedal width in cm.",
  "Iris species."
)
iris_schema$fields <- purrr::imap(
  iris_schema$fields,
  ~ c(.x, description = descriptions[.y])
)

str(iris_schema)
```

(c) Anja: geeft mogelijkheid om mijn csv's met metadata in te laden en zo toe te kennen 
aan de verschillende velden
Els Lommelen heeft code waarbij toewijzing gebeurt obv veldnaam ipv positie.



## Export

Now that you have created your Data Package, you can write it to a directory of your 
choice with `write_package()`.

```{r}
write_package(my_package, "my_directory")
```

The directory will contain four files: the descriptor `datapackage.json`, 
one CSV file containing the data for the resource `iris` and two CSV files 
containing the data for the resource `observations`.

```{r}
list.files("my_directory")
#> [1] "datapackage.json"   "iris.csv"           "observations_1.csv"
#> [4] "observations_2.csv"
```


The frictionless pkg does not provide functionality to deposit your Data Package on 
a research repository such as Zenodo, but here are some tips:   

1. Validate your Data Package before depositing. You can do this in Python with the 
Frictionless Framework using frictionless validate datapackage.json.    

2. Zip the individual CSV files (and update their paths in datapackage.json) to reduce size, 
not the entire Data Package. That way, users still have direct access to the 
datapackage.json file. See `this example`(https://zenodo.org/records/5061303#files).     

3. Only describe the technical aspects of your dataset in datapackage.json 
(fields, units, the dataset identifier in id). 
Authors, methodology, license, etc. are better described in the metadata fields 
the research repository provides.   







